\chapter*{Acknowledgments}
First and foremost I thank my advisor, mentor, and dissertation chair, Richard Wright.  For the last three years he has (among other things) challenged, inspired, critiqued, funded, encouraged, frustrated, and befriended me.  One of the main reasons I finished graduate school was that I truly enjoyed going to our meetings.  Sharon Hargus has also been a generous and understanding presence, and I am grateful for the guidance she has provided and the example of uncompromising integrity that she sets.

I owe a large debt to the other members of my dissertation committee, Erick Gallun and Gina-Anne Levow, who raised keen questions and offered seasoned advice along the way, and struggled through my inelegant draft prose to help refine this work.  I would be remiss if I failed to also mention Pam Souza, who has been a great collaborator, and a model example of science in the service of humanity.  Jennifer Haywood, Gus McGrath, and Heather Morrison get special mention here as well for their work on the \ac{pnnc} corpus; Gus in particular for having so quickly transitioned from student to trainee to collaborator, and for doing so much of the dirty work that makes a spoken corpus fit for public consumption.

My colleagues in the UW Linguistics Department have been fine companions, and I have profited from many stimulating discussions over the years.  Special thanks go to Josh Crowgey, Valerie Freeman, Justin Goodenkauf, Michael Goodman, Prescott Klassen, Bill McNeill, Julia Miller, Meghan Oxley, Sarala Puthuval, John Riebold, Lisa Tittle, and most especially Darren Tanner and Steve Moran.  Most of my conversations with these folks had little to do with my dissertation research, but rather were a source of enrichment and distraction when it was sorely needed.  To the extent that I seem like a well-rounded scholar, it is often because of the little facets of knowledge that I gleaned from each of them.  

I must also acknowledge my dear friends outside of academia, who for several years have tolerated my absence from parties, dinners, concerts, openings, performances and festivals, and yet still embraced me fondly when I did manage to show up once in a while.  My parents have been especially tolerant in this regard, and deserve thanks for so much more than I can describe here.

Along my winding path through education, I have had a number of gifted teachers who quietly inspired me to remain curious and to someday be as good a teacher as they were.  I have always wanted to acknowledge them publicly; this seems as good a place as any.  Thanks to (in chronological order): Sherry Brown (chemistry), David Adams (calculus), Dennis Lamb (Greek and Roman literature), Bill Moody (cellular neurobiology), Larry BonJour (epistemology), Bill Talbott (moral and social philosophy), David Knechteges (Chinese literature), Bi Nyan-Ping (Chinese language), Zev Handel (Chinese historical linguistics), and Chris Stecker (psychoacoustics).
